%% -------------------------------------------------
%%      LEARNING
%% -------------------------------------------------

\cvsection{Learning}
\begin{itemize}
    \item[--] \textbf{DEV210.3X: ADVANCED C++} \,Proficiency course on C++ by Microsoft through edX.\\Certificate ID: 039bfc5200834992a5170f8b0d2195b6 (Nov. 2018)
    \item[--] \textbf{Attended Workshop on Cyber Security} \,By Arvind Singh, Sr. Security Consultant at IBM India Private Limited (Oct. 2018)
\end{itemize}

%% -------------------------------------------------
%%      INTERESTS
%% -------------------------------------------------

\cvsection{Interests}
\cvtag{Arduino} 
\cvtag{Electronics}
\cvtag{Computers}\\[3pt]
\cvtag{Problem Solving}
\cvtag{Music}

%% -------------------------------------------------
%%      RESEARCH WORK
%% -------------------------------------------------

\cvsection{Research Work}
\cvproject{Indoor Navigation For All (INFA) (10/2017 - 02/2018)}
\begin{itemize}
\item An advanced solution to users around the world who find it difficult to navigate in places such as metro stations and airports. It aims to empower visually impaired with the help of beacon technology to identify the precise location of the user and provide the information such as nearby points of interests. Cleared for first round at Saint Gobain Scholarship on 26 Feb 2018.
\end{itemize}
\smallskip
\cvproject{Portable Air Conditioner (09/2015 - 12/2015)}
\begin{itemize}
\item An Innovative approach to affordable air conditioning for user who cannot afford an A/C or the electricity costs, where the which targets the specific use of an A/C that is while sleeping, by cooling only the bed and its surroundings. A prototype for which was also made. Presented at CBSE Science Exhibition, state level on 17-19 Dec 2015.
\end{itemize}

%% -------------------------------------------------
%%      CAREER INTERESTS
%% -------------------------------------------------

\cvsection{Career Interests}
\cvtag{IOT}
\cvtag{Systems}
\cvtag{Cloud Computing}\\[3pt]
\cvtag{Cyber Security}
\cvtag{Artificial Intelligence}\\[3pt]
\cvtag{Bio Computing}